Bee visitation, pollination service, and plant yield in commodity and hybrid seed canola

### 2023-02-09 Manuscript/manuscript_files/supplemental.tex
Finished revisions, and added DryadData folder

%  & Pods per plant & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\

@@

% \multirow{-6}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\

@@

%  & Pods per plant & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\

@@

%  & Pods per plant & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\

@@

 & Pods per plant & -0.162 & 0.013 & $<$0.0001 & -0.136* & -0.242*\\

@@

\multirow{-5}{*}{\raggedright\arraybackslash Pods per plant} & Phi & 3.346 & 0.067 & - & 3.036* & 3.975*\\

@@

 & Pods per plant & 0.557 & 0.288 & 0.0529 & 0.722 & 0.623\\

@@

 & Pods per plant & 0.108 & 0.045 & 0.0159 & 0.126 & 0.042\\

@@

%  & Pods per plant & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\

@@

% \multirow{-11}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.22 & 0.12 & 0.22 & -0.01 & 0.44 & - & 2538 & 1.003\\

@@

%  & Pods per plant & 1.65 & 0.35 & 1.65 & 0.94 & 2.34 & $<$0.0001 & 2485 & 1.001\\

@@

 & Pods per plant & -0.141 & 0.012 & $<$0.0001 & -0.215* & -0.118*\\

@@

\multirow{-9}{*}{\raggedright\arraybackslash Pods per plant} & Plant size (Phi) & 0.222 & 0.115 & - & 0.492 & -0.032\\

@@

 & Pods per plant & 1.647 & 0.352 & $<$0.0001 & 3.201 & 1.305\\

@@

Formulas for total yield models are  using \texttt{lmer}-style R formulas. Predicted yield for each plant was calculated as: pods per plant $\times$ seeds per pod $\times$ weight per seed. Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random intercepts (and slopes).

>>>>

%  & \% Pod Set & -0.16 & 0.01 & -0.16 & -0.19 & -0.14 & $<$0.0001 & 2108 & 1.003\\

@@

% \multirow{-6}{*}{\raggedright\arraybackslash \% Pod Set} & Phi & 3.35 & 0.07 & 3.35 & 3.21 & 3.48 & - & 3828 & 1.003\\

@@

%  & \% Pod Set & 0.56 & 0.29 & 0.56 & 0.00 & 1.12 & 0.0529 & 4888 & 0.999\\

@@

%  & \% Pod Set & 0.11 & 0.04 & 0.11 & 0.02 & 0.19 & 0.0159 & 3037 & 1.000\\

@@

 & \% Pod Set & -0.162 & 0.013 & $<$0.0001 & -0.136* & -0.242*\\

@@

\multirow{-5}{*}{\raggedright\arraybackslash \% Pod Set} & Phi & 3.346 & 0.067 & - & 3.036* & 3.975*\\

@@

 & \% Pod Set & 0.557 & 0.288 & 0.0529 & 0.722 & 0.623\\

@@

 & \% Pod Set & 0.108 & 0.045 & 0.0159 & 0.126 & 0.042\\

@@

%  & \% Pod Set & -0.14 & 0.01 & -0.14 & -0.17 & -0.12 & $<$0.0001 & 5503 & 0.999\\

@@

% \multirow{-11}{*}{\raggedright\arraybackslash \% Pod Set} & Plant size (Phi) & 0.22 & 0.12 & 0.22 & -0.01 & 0.44 & - & 2538 & 1.003\\

@@

%  & \% Pod Set & 1.65 & 0.35 & 1.65 & 0.94 & 2.34 & $<$0.0001 & 2485 & 1.001\\

@@

 & \% Pod Set & -0.141 & 0.012 & $<$0.0001 & -0.215* & -0.118*\\

@@

\multirow{-9}{*}{\raggedright\arraybackslash \% Pod Set} & Plant size (Phi) & 0.222 & 0.115 & - & 0.492 & -0.032\\

@@

 & \% Pod Set & 1.647 & 0.352 & $<$0.0001 & 3.201 & 1.305\\

@@

Formulas for total yield models are  using \texttt{lmer}-style R formulas. Predicted yield for each plant was calculated as: \% Pod Set $\times$ flowers per plant $\times$ seeds per pod $\times$ weight per seed. Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random intercepts (and slopes).
